### 2011-05-23 tags/crisp-1.1.6/tags/ant-crisp/Papers/crisp-rtg-09/crisp-rtg-09.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

\section{Introduction}

@@

\section{Conclusion}

>>>>

\section{Introduction} \label{sec:introduction}

In \citet{KolSto07}, Matthew Stone and I showed how the sentence
generation problem of TAG grammars can be encoded into a planning
problem. A planner could then be used to compute a plan, and this plan
could be decoded into a TAG derivation, and further into a sentence.

In this manuscript, I generalize this result to sentence generation
with regular tree grammars \citep{tata2007}.  Our older TAG encoding
is indeed a special case of this because it is known that for each TAG
grammar, the language of derivation trees forms a regular tree
language \citep{schmitz08:_featur_in_tag_deriv_trees}. On the other
hand, there are many other grammar formalisms whose derivational
structures can be seen as regular tree languages -- including regular
dependency grammars \citep{kuhlmann2007mildly}, linear context-free
rewrite systems
\citep{weir88:_charac_mildl_contex_sensit_gramm_formal}, and
combinatory categorial grammars
\citep{steedman01:_syntac_proces,KolKuh09}. What distinguishes these
grammar formalisms from each other is how they assign word order to
the trees in the regular tree language. But as long as we can read the
trees we generate with our RTG as having each node decorated with
lexicon entries of the underlying grammar formalism, we can leave it
up to the grammar formalism to compute the word order (e.g., by
computing a derived tree from a TAG derivation tree and reading the
leaves left to right). As a consequence, the construction in this
paper generalizes our sentence-generation-as-planning approach to a
whole range of mildly context-sensitive grammar formalisms.

The paper is structured as follows. In
Section~\ref{sec:gener-probl-regul}, I will define the sentence
generation problem of regular tree grammars and illustrate it with an
example. In Section~\ref{sec:rtg-generation-as-planning}, I will
sketch how to adapt the planning construction by \citet{KolSto07} to
regular tree grammars. In Section~\ref{sec:np-completeness}, I prove
that the sentence generation problem of RTGs is NP-complete, which
justifies the use of a worst-case exponential algorithm like a planner
for solving the problem. Section~\ref{sec:conclusion} concludes and
points to future work.

@@

\section{Conclusion}
\label{sec:conclusion}

### 2011-05-23 tags/crisp-1.1.6/tags/ant-crisp/Papers/dl-gre-jair/related.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

Viewing GRE as a problem of generating DL formulas offers a unified
perspective: It is the problem of computing a DL
formula with a given extension.  Many existing approaches can be
subsumed under this view; we have summarized this for some of them in
Fig.~\ref{fig:related}, along with the DL fragment they use.  We
already discussed some of these approaches in Section~\ref{sec:gre}.
Furthermore, the non-relational but negative and disjunctive
descriptions generated by \newcite{deemter02:_gener_refer_expres} are
simply formulas of $\mathcal{PL}$; and
\newcite{gardent02:_gener_minim_defin_descr} generalizes this into
generating formulas of $\mathcal{ELU}_{(\neg)}$, i.e., \el\ plus
disjunction and atomic negation.  The approach presented here fits
well into this landscape, and it completes the picture by showing how
to generate REs in \alc, which combines all connectives used in any of
these previous approaches.

Where our approach breaks new ground is in the way these formulas are
computed: It successively refines a decomposition of the domain into
subsets.  In this way, it is reminiscent of the Incremental Algorithm,
which in fact can be seen as the special case of the \el\ algorithm.
However, unlike
\newcite{dale91:_gener_refer_expres_invol_relat} and its successors,
such as \newcite{kelleher06:_increm_gener_of_spatial_refer},
we do not have to take special precautions to avoid infinite
regress. While Dale and Haddock's algorithm attempts to generate a RE
for a single individual, for successive individuals in the model, our
algorithms consider all individuals in parallel.  It monotonically
refines a partition of the model and never needs to backtrack, and
therefore is always guaranteed to terminate.

\begin{figure}
  \centering
  \begin{small}
  \begin{tabular}{l|p{0.2\textwidth}}
    GRE algorithm & DL variant \\ \hline
    \newcite{Dale1995} & $\mathcal{CL}$ \\
    \newcite{deemter02:_gener_refer_expres} & $\mathcal{PL}$ \\
    \newcite{dale91:_gener_refer_expres_invol_relat} & \el \\
    \newcite{kelleher06:_increm_gener_of_spatial_refer} & \el \\
    \newcite{gardent02:_gener_minim_defin_descr} & $\mathcal{ELU}_{(\neg)}$\\
%    \newcite{Krahmer2003} & \el\ + equality between individuals
  \end{tabular}
  \end{small}
  \caption{DL variants used by different GRE algorithms.}
  \label{fig:related}\vspace*{-1.5ex}
\end{figure}

>>>>

Viewing GRE as a problem of generating DL formulas offers a unified
perspective: It is the problem of computing a DL
formula with a given extension.  Many existing approaches can be
subsumed under this view; we have summarized this for some of them in
Fig.~\ref{fig:related}, along with the DL fragment they use.  We
already discussed some of these approaches in Section~\ref{sec:gre}.
Furthermore, the non-relational but negative and disjunctive
descriptions generated by \citeA{deemter02:_gener_refer_expres} are
simply formulas of $\mathcal{PL}$; and
\citeA{gardent02:_gener_minim_defin_descr} generalizes this into
generating formulas of $\mathcal{ELU}_{(\neg)}$, i.e., \el\ plus
disjunction and atomic negation.  The approach presented here fits
well into this landscape, and it completes the picture by showing how
to generate REs in \alc, which combines all connectives used in any of
these previous approaches.

Where our approach breaks new ground is in the way these formulas are
computed: It successively refines a decomposition of the domain into
subsets.  In this way, it is reminiscent of the Incremental Algorithm,
which in fact can be seen as a special case of the \el\ algorithm.
However, unlike \citeA{dale91:_gener_refer_expres_invol_relat} and
its successors, such as
\citeA{kelleher06:_increm_gener_of_spatial_refer}, we do not have to
take special precautions to avoid infinite regress. While Dale and
Haddock's algorithm attempts to generate a RE for a single individual,
for successive individuals in the model, our algorithms consider all
individuals in parallel.  It monotonically refines a partition of the
model and never needs to backtrack, and therefore is always guaranteed
to terminate.

\begin{figure}
  \centering
  \begin{small}
  \begin{tabular}{l|p{0.2\textwidth}}
    GRE algorithm & DL variant \\ \hline
    \citeA{Dale1995} & $\mathcal{CL}$ \\
    \citeA{deemter02:_gener_refer_expres} & $\mathcal{PL}$ \\
    \citeA{dale91:_gener_refer_expres_invol_relat} & \el \\
    \citeA{kelleher06:_increm_gener_of_spatial_refer} & \el \\
    \citeA{gardent02:_gener_minim_defin_descr} & $\mathcal{ELU}_{(\neg)}$\\
%    \citeA{Krahmer2003} & \el\ + equality between individuals
  \end{tabular}
  \end{small}
  \caption{DL variants used by different GRE algorithms.}
  \label{fig:related}\vspace*{-1.5ex}
\end{figure}

### 2011-05-23 tags/crisp-1.1.6/tags/spark-08-submit/discussion.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

The positive conclusion we can draw from the simple experiments
reported above is that modern planners are fairly good at controlling
the search for many of the moderately-sized NLG problems we looked
at. This is particularly true for FF in the sentence generation
domain, which generates nontrivial 14-word sentences in about two seconds.
There is still room for improvement, however: special-purpose
algorithms generate much larger referring expressions in
milliseconds \cite{AreKolStr08}.  Although search efficiency is not the
main concern in these domains, it nevertheless becomes a factor in
scenarios like Experiment~2, where the world is almost completely
unconstrained and (unsurprisingly) the search becomes much slower.

The most restrictive bottleneck in the two domains we investigated is
the initial grounding step that many modern planners perform. While
this may be a good strategy for traditional planning benchmarks and
IPC domains---where plan length often dominates universe size, and an
initial investment into grounding pays off in saved instantiations
during the search---this approach is less effective in the domains
we've considered. As our experiments show, there are natural
planning domains in which relatively short plans must be computed in
large universes. For instance, in the case of the sentence generation
domain, it is not unrealistic to look for plans of length 20 over a
universe consisting of thousands of domain individuals and tens of
thousands of actions, some of which require three domain individuals
as parameters. The common strategy of splitting the universe over
several types of individuals will not be very effective here.

The recent trend in planning research has (rightfully) focused on the
development of algorithms that control search in sophisticated ways,
resulting in a host of planners that are more powerful and more
successful than their predecessors. However, the common strategy of
grounding out sets of predicates and actions in implementations of these
algorithms has a very pronounced effect on domains such as those described
above. More sophisticated techniques based on reachability analysis may
have the potential to help improve this situation, provided such
approaches can avoid the drawbacks resulting from unnecessary grounding.
Since our domains are not that unusual in their structure and composition,
we hope that the lessons learnt from our experiences can help improve the
performance of current systems.  We believe that such improvements are
necessary if planning is to become a more mature technology that can offer
tools to a wider community of users.  At the end of the day, real-world
users will care about the \emph{total} runtime of a planner, and this is
more than just the search time.
%has the potential to help---we could gain a lot by only computing
%reachable instances---, but this too is typically done on the grounded
%problem.  \todo{check if this is true}

@@

>>>>

The positive conclusion we can draw from the simple experiments
reported above is that modern planners are fairly good at controlling
the search for many of the moderately-sized NLG problems we looked
at. This is particularly true for FF in the sentence generation
domain, which generates nontrivial 14-word sentences in about two
seconds. There is still room for improvement, however; special-purpose
algorithms generate much larger referring expressions in milliseconds
\cite{AreKolStr08}.  Although search efficiency is not the main
concern in these domains, it nevertheless becomes a factor in
scenarios like Experiment~2, where the world is almost completely
unconstrained and (unsurprisingly) the search becomes much slower.

%The positive conclusion we can draw from the experiments reported
%above is that for the most part, modern planners are pretty good at
%controlling the search for the NLG-related inputs that we looked at.
%This is particularly true for FF in the sentence generation domain,
%which generates nontrivial 14-word sentences in about two seconds.
%There is still room for improvement (a special-purpose algorithm for
%referring expressions could generate ten of these 14 words in a few
%milliseconds), and the search becomes slower -- for obvious reasons --
%in the almost completely unconstrained world of Experiment 2, but
%search is not the main efficiency bottleneck.

The most restrictive bottleneck in the two domains we investigated is the
initial grounding step that many modern planners perform. While this may be
a good strategy for traditional planning benchmarks and IPC domains---where
plan length often dominates universe size, and an initial investment into
grounding pays off in saved instantiations during the search---this
approach is less effective in the domains we've considered. As our
experiments have shown, there are natural planning domains in which
relatively short plans must be computed in large universes. For instance,
in the case of the sentence generation domain, it is not unrealistic for
the universe to consist of thousands of domain individuals and tens of
thousands of actions, some of which require three domain individuals as
parameters. The common strategy of splitting the universe over several
types of individuals will not be very effective here.

%The most restrictive bottleneck in the two domains we have looked at
%in this paper is the initial grounding step that almost all modern
%planners perform.  Our conclusion from the experiments reported above
%is that this is a good strategy in domains where the typical plan
%length dominates the typical universe size, i.e.\ where the initial
%investment into grounding pays off in saved unifications during the
%search.  However, as we have shown, there are natural planning domains
%in which relatively short plans must be computed in large universes;
%it is not unrealistic for the universe in the sentence generation
%domain to consist of thousands of domain individuals and tens of
%thousands of actions, some of which take three domain individuals as
%parameters.  The common strategy of splitting the universe over
%several types of individuals will not be very effective here.

The recent trend in planning research has (rightfully) focused on the
development of algorithms that control search in sophisticated ways,
resulting in a host of planners that are more powerful and more
successful than their predecessors. However, the common strategy of
grounding out sets of predicates and actions in implementations of
these algorithms has a very pronounced effect on domains such as those
described above. Since our domains are not that unusual in their
structure and composition, we hope that the lessons learnt from our
experiences can help improve the performance of current systems. We
believe that such improvements are necessary if planning is to become
a more mature technology that can offer tools to a wider community of
users. At the end of the day, real-world users will care about the
\emph{total} runtime of a planner, and this is more than just the
search time.
%We offer our larger problem instances as future challenges for the
%planning community.

%We believe that if planning is to become a mature technology which
%real-world users will believe in, it must find a way to deal with the
%grounding problem more gracefully than current systems do.  The
%research focus in developing planning algorithms has quite rightfully
%been on dealing with the search, and for this it is convenient --
%depending on the particular algorithm, necessary -- to ground out all
%predicates and actions before starting the search itself.  However, we
%think that the domains presented here are not that unusual in their
%ratio of plan length against universe size.  At the end of the day,
%real-world users will care about the \emph{total} runtime of a
%planner, and this is more than just the search.

@@

%By and large, it is a relatively pleasant experience to come as a
%``customer'' to the planning community: Thanks to the competitions, it
%is easy to identify and download a fast implementation, at least for
%Linux.  However, in the course of our experiments we found (and
%reported) bugs in both SGPLAN and FF.  And as our experiments have
%shown, there is no one silver bullet: Even planners as closely related
%as FF and SGPLAN can differ significantly in their performance on
%different domains.

### 2011-05-23 tags/crisp-1.1.6/tags/spark-08-submit/domains.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

The process described above has clear parallels to planning: we
manipulate a state by applying actions in order to achieve a goal. We
can make this connection even more precise by translating the SPUD
problem into a planning problem.\footnote{See
  \url{http://code.google.com/p/crisp-nlg/} for the CRISP system, in
  which this conversion is implemented.}  For instance,
Figure~\ref{fig:white-rabbit-as-planning} shows the corresponding PDDL
actions for the above generation task, where each action corresponds
to an operation that adds a single elementary tree to the derivation.
In each case, the first parameter of the action is a node name in the
derivation tree, and the remaining parameters stand for the
individuals to which the semantic roles will be instantiated.  The
syntactic preconditions and effects are encoded using $\mathsf{open}$
and $\mathsf{canadjoin}$ literals; the status of each referring
expression is tracked using $\mathsf{distractor}$ literals. Notice
that the action effects contain terms of the form $\mathsf{subj}(u)$,
which construct new node names. In order to meet the syntactic
requirements of PDDL, these terms can be eliminated by estimating an
upper bound $n$ for the plan length, making $n$ copies of each action,
ensuring that copy $i$ can only be applied in step $i$, and replacing
the term $\mathsf{subj}(u)$ in an action copy by the constant
$\mathsf{subj}_i$.

Once the appropriate actions are defined, we can solve the generation
problem as an ordinary planning problem. For instance, the following plan
solves our previous example:
%
\begin{enumerate}
\item $\mathsf{sleeps}(\mathsf{root}, r_1)$,
\item $\mathsf{rabbit}(\mathsf{subj}(\mathsf{root}), r_1)$,
\item $\mathsf{white}(\mathsf{subj}(\mathsf{root}), r_1)$.
\end{enumerate}
%
Using this plan, the grammatical derivation in
Figure~\ref{fig:white-rabbit-sleeps-deriv}, and therefore the
generated sentence ``the white rabbit sleeps'', can be systematically
reconstructed. Thus, we can solve the sentence generation problem via
the detour through planning and bring current search heuristics for
planning to bear on generation.

@@

The object of the GIVE Challenge (``Generating Instructions in Virtual
Environments''; Koller et al.\
\citeyear{alexander07:_shared_task_propos}) is to build an NLG system
which is able to produce natural-language instructions which will
guide a human user in performing some task in a virtual
environment. From an NLG perspective, GIVE makes for an interesting
challenge because it is a theory-neutral task that exercises all
components of an NLG system, and emphasizes the study of communication
in a (simulated) physical environment. It also has the advantage that
the user and the NLG system can be in physically different places, as
long as the 3D client and the NLG system are connected over a
network. This makes it possible to evaluate GIVE NLG systems on a
large scale over the Internet. The first GIVE evaluation will take
place in late 2008; currently eight research teams from five countries
are working on developing systems to participate in the
challenge.\footnote{See the GIVE website for more details about this
  project: \url{http://www.give-challenge.org/}.}

@@

A map of an example GIVE world is shown in
Figure~\ref{fig:give-development-world}.  In this world, the user's
task is to pick up a trophy in the top left room.  The trophy is
hidden in a safe behind a picture, so the user must first move the
picture out of the way and open the safe by pushing a sequence of
buttons (the small square boxes on the walls) in the correct order.
In order to get to all these buttons, the user must also open the door
in the centre of the map and deactivate the alarm tile by pushing
further buttons.  To simplify both the planning and the NLG task, the
world is discretised into tiles of equal size; the user can turn by 90
degree steps in either direction, and can move from the centre of one
tile to the centre of the next. Figure~\ref{fig:give-planning} shows
some of the available actions in PDDL syntax.

@@

The plans generated in the GIVE domain are often nontrivial. For instance,
in the above example the shortest plan consists of 108 action steps; the
first few steps are as follows:
%
\begin{enumerate}
\item $\mathsf{turn}\textsf{-}\mathsf{left}(\mathsf{north},
\mathsf{west})$,
\item $\mathsf{move}(\mathsf{pos\_5\_2}, \mathsf{pos\_4\_2}, \mathsf{west})$,
\item $\mathsf{manipulate}\textsf{-}\mathsf{b1}\textsf{-}\mathsf{off}\textsf{-}\mathsf{on}(\mathsf{pos\_5\_2})$,
\item $\mathsf{turn}\textsf{-}\mathsf{right}(\mathsf{west}, \mathsf{north})$.
\end{enumerate}

@@

The GIVE task comes with a number of interesting research challenges
both for the NLG and the planning communities.  On the NLG side, one
major problem is that the natural language instruction sequences can't
simply be obtained by verbalising each action instance in a plan in turn.
For instance, the NLG system could generate an instruction sequence
starting with ``turn left; walk forward; press the button; turn right; walk
forward; walk forward; turn right; walk forward; walk forward; turn left;
walk forward''.  However, such directions would be clumsy and boring, and
it is to be expected that frustrated users will quickly cancel an
interaction with such a system, resulting in a bad evaluation score.
Having just pressed the button, it would be much better to say ``turn
around and walk through the door''. That is, plans must be
\emph{summarised} by merging multiple action instances into a single
instruction, in order to present them to the
user.\footnote{This task is similar to the construction of ``macro''
actions, but is primarily intended for plan presentation.}
Conversely, it may also be necessary to \emph{elaborate} on a single
planning step by expressing it with several instructions.  Having just
entered the top left room, it may be easier for the user to understand the
instruction ``walk to the centre of the room; turn right; now press the
green button in front of you'', rather than the instruction ``press the
green button on the wall to your right''.  To plan the referring expression
``the green button in front of you'' at a time when the button is not yet
in front of the user, the NLG system must keep track of the hypothetical
changes in what objects are visible to the user.  Thus the acts of
referring and instructing, and the modules for planning and NLG, must be
tightly integrated.

>>>>

The process described above has clear parallels to planning: we manipulate
a state by applying actions in order to achieve a goal. We can make this
connection even more precise by translating the SPUD problem into a
planning problem. For instance, Figure~\ref{fig:white-rabbit-as-planning}
shows the corresponding PDDL actions for the above generation task, where
each action corresponds to an operation that adds a single elementary tree
to the derivation.  In each case, the first parameter of the action is a
node name in the derivation tree, and the remaining parameters stand for
the individuals to which the semantic roles will be instantiated.  The
syntactic preconditions and effects are encoded using $\mathsf{open}$ and
$\mathsf{canadjoin}$ literals; the status of each referring expression is
tracked using $\mathsf{distractor}$ literals. Notice that the action
effects contain terms of the form $\mathsf{subj}(u)$, which construct new
node names. In order to meet the syntactic requirements of PDDL, these
terms can be eliminated by estimating an upper bound $n$ for the plan
length, making $n$ copies of each action, ensuring that copy $i$ can only
be applied in step $i$, and replacing the term $\mathsf{subj}(u)$ in an
action copy by the constant $\mathsf{subj}_i$.

Once the appropriate actions are defined, we can solve the generation
problem as an ordinary planning problem. For instance, the following plan
solves our previous example:
%
\begin{enumerate}
\item $\mathsf{sleeps}(\mathsf{root}, r_1)$
\item $\mathsf{rabbit}(\mathsf{subj}(\mathsf{root}), r_1)$
\item $\mathsf{white}(\mathsf{subj}(\mathsf{root}), r_1)$
\end{enumerate}
%
Using this plan, the grammatical derivation in
Figure~\ref{fig:white-rabbit-sleeps-deriv}, and therefore the generated
sentence, can be systematically reconstructed. Thus, we can solve the
sentence generation problem via the detour through planning and bring
current search heuristics for planning to bear on generation.

@@

The object of the GIVE Challenge (``Generating Instructions in Virtual
Environments''; Koller et al.\ \citeyear{alexander07:_shared_task_propos})
is to build an NLG system which is able to produce natural-language
instructions which will guide a human user in performing some task in a
virtual environment. From an NLG perspective, GIVE makes for an
interesting challenge because it is a theory-neutral task that exercises
all components of an NLG system, and emphasizes the study of communication
in a (simulated) physical environment. It also has the advantage that the
user and the NLG system can be in physically different places, as long as
the 3D client and the NLG system are connected over a network. This makes
it possible to evaluate GIVE NLG systems on a large scale over the
Internet. The first GIVE evaluation will take place in late 2008;
currently eight research teams from five countries are working on
developing systems to participate in the challenge.\footnote{See the GIVE
 website for more details about this project:
 \url{homepages.inf.ed.ac.uk/v1akolle/proj/give/}.}

@@

A map of an example GIVE world is shown in
Figure~\ref{fig:give-development-world}.  In this world, the user's
task is to pick up a trophy in the top left room.  The trophy is
hidden in a safe behind a picture, so the user must first move the
picture out of the way and open the safe by pushing a sequence of
buttons (the small square boxes on the walls) in the correct order.
In order to get to all these buttons, the user must also open the door
in the centre of the map and deactivate the alarm tile by pushing
further buttons.  To simplify both the planning and the NLG task, the
world is discretized into tiles of equal size; the user can turn by 90
degree steps in either direction, and can move from the centre of one
tile to the centre of the next. Figure~\ref{fig:give-planning} shows
some of the available actions in PDDL syntax.

@@

The plans generated in the GIVE domain are often nontrivial. For instance,
in the example above the shortest plan consists of 108 action steps; the
first few steps are as follows:
%
\begin{enumerate}
\item $\mathsf{turn}\textsf{-}\mathsf{left}(\mathsf{north}, \mathsf{west})$
\item $\mathsf{move}(\mathsf{pos\_5\_2}, \mathsf{pos\_4\_2}, \mathsf{west})$
\item $\mathsf{manipulate}\textsf{-}\mathsf{b1}\textsf{-}\mathsf{off}\textsf{-}\mathsf{on}(\mathsf{pos\_5\_2})$
\item $\mathsf{turn}\textsf{-}\mathsf{right}(\mathsf{west}, \mathsf{north})$
\end{enumerate}

@@

The GIVE task comes with a number of interesting research challenges
both for the NLG and the planning communities.  On the NLG side, one
major problem is that the natural language instruction sequences can't
simply be obtained by verbalising each action instance in a plan in
turn.  For instance, the NLG system could generate an instruction
sequence starting with ``turn left; walk forward; press the button;
turn right; walk forward; walk forward; turn right; walk forward; walk
forward; turn left; walk forward''.  However, this would be clumsy and
boring, and it is to be expected that frustrated users will quickly
cancel an interaction with such a system, resulting in a bad
evaluation score.  Having just pressed the button, it would be much
better to say ``turn around and walk through the door''; i.e.,
multiple action instances should be merged into a single
instruction. Conversely, it may also be necessary to express a single
planning step with several instructions.  Having just entered the top
left room, it may be easier for the user to understand the instruction
``walk to the centre of the room; turn right; now press the green
button in front of you'' than the instruction ``press the green button
on the wall to your right''.  To plan the referring expression ``the
green button in front of you'' at a time when the button is not yet in
front of the user, the NLG system must keep track of the hypothetical
changes in what objects are visible to the user.  Thus the acts of
referring and instructing, and the modules for planning and NLG, must
be tightly integrated.

### 2011-05-23 tags/crisp-1.1.6/tags/spark-08-submit/introduction.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

We then discuss some of our experiences using off-the-shelf planners in our
two domains. In particular, we explore the efficiency of FF
\cite{HoffmannNebel01} and SGPLAN
\cite{hsu06:_new_featur_in_sgplan_for}---planners that are easily
available, support an expressive subset of PDDL for encoding preconditions
and effects, and have been successful on traditional benchmarks and in the
International Planning Competition (IPC)---on a range of problem instances
from our planning domains.  We also compare these results against an ad-hoc
Java implementation of GraphPlan \cite{Blum1997}.  Our findings are mixed.
On the one hand, it turns out that modern planners handle some of the
search problems that arise in NLG quite easily (although large problem
instances still remain a challenge).  On the other hand, these same
planners spend tremendous amounts of time on preprocessing. For instance,
FF spends 90\% of its runtime in the sentence generation domain on
grounding out literals and actions, and ends up slower than our version of
GraphPlan that avoids grounding. For domains like ours, which are dominated
by the number of actions and the universe size, rather than the
combinatorics of the search problem, this observation suggests that the
overall runtime of a planner could be improved by grounding more
selectively. We therefore offer these domains as challenges for the
planning community.
%available, support expressive preconditions and effects out of the box,

>>>>

We then discuss some of our experiences using off-the-shelf planners
in our two domains. In particular, we explore the efficiency of FF
\cite{HoffmannNebel01} and SGPLAN
\cite{hsu06:_new_featur_in_sgplan_for}---planners that have been successful
on traditional benchmarks, and in the International Planning Competition
(IPC)---on a range of problem instances from our planning domains.  We also
compare these results against an ad-hoc Java implementation of GraphPlan
\cite{Blum1997}.  Our findings are mixed. On the one hand, it turns out
that modern planners handle some of the search problems that arise in NLG
quite easily (although large problem instances still remain a challenge).
On the other hand, these same planners spend tremendous amounts of time on
preprocessing. For instance, FF spends 90\% of its runtime in the sentence
generation domain on grounding out literals and actions, and ends up slower
than our version of GraphPlan that avoids grounding. For domains like ours,
which are dominated by the number of actions and the universe size, rather
than the combinatorics of the search problem, this observation suggests
that the overall runtime of a planner could be improved by grounding more
selectively. We therefore offer these domains as challenges for the
planning community.

### 2011-05-23 tags/crisp-1.1.6/trunk/Papers/ci-spark/abstract.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

\begin{abstract}
  Natural language generation (NLG) is a major subfield of
  computational linguistics with a long tradition as an application
  area of automated planning systems. While the connection between
  NLG and planning has not received much attention in current
  mainstream NLG research, several recent publications have sparked
  a renewed interest in this area. In this paper, we investigate the
  extent to which these new NLG approaches profit from the advances
  in planner expressiveness and efficiency. Our findings are mixed.
  While modern planners can readily handle the search problems that
  arise in our NLG experiments, their overall runtime is often
  dominated by the grounding step they perform as preprocessing.
  Furthermore, small changes in the structure of a domain can
  significantly shift the balance between search and preprocessing.
  Overall, our experiments show that the off-the-shelf planners we
  tested are unusably slow for nontrivial NLG problem instances. As
  a result, we offer our domains and experiences as challenges for
  the planning community.
\end{abstract}

>>>>

\begin{abstract}
  Natural language generation (NLG) is a major subfield of
  computational linguistics with a long tradition as an application
  area of automated planning systems. While things were relatively
  quiet with the planning approach to NLG for a while, several recent
  publications have sparked a renewed interest in this area. In this
  paper, we investigate the extent to which these new NLG approaches
  profit from the advances in planner expressiveness and
  efficiency. Our findings are mixed.  While modern planners can
  readily handle the search problems that arise in our NLG
  experiments, their overall runtime is often dominated by the
  grounding step they perform as preprocessing.  Furthermore, small
  changes in the structure of a domain can significantly shift the
  balance between search and preprocessing.  Overall, our experiments
  show that the off-the-shelf planners we tested are unusably slow for
  nontrivial NLG problem instances. As a result, we offer our domains
  and experiences as challenges for the planning community.
\end{abstract}

### 2011-05-23 tags/crisp-1.1.6/trunk/Papers/crisp-ff-10/introduction.tex
[maven-release-plugin]  copy for tag crisp-1.1.6

In this paper, we revisit this situation, and analyze the sources of
inefficiency in detail for FF. Based on the analysis, we modify FF and
obtain dramatically better performance that, for the first time, makes
automated planners a realistic possibility for NLG applications. To
achieve this quantum leap, all that is needed are a few minor
implementation fixes and basic reconfiguration of search
options. While these fixes certainly are no contribution to planning
in their own right, we consider it a valuable -- and slightly
unsettling -- lesson learned that such banalities can make the
difference between success and failure. They can hold up progress in
planning applications for years, unless users of a planner have direct
access to its developer. We interpret this as illustrative of the
importance of implementation details such as the preprocessor for the
overall runtime, and as a strong call for automated configuration
techniques, e.g.\ along the lines of Hutter et al.\
\shortcite{HutHooStu07}.

>>>>

In this paper, we revisit this situation, and analyze the sources of
inefficiency in detail for FF. Based on the analysis, we modify FF and
obtain dramatically better performance that, for the first time, makes
automated planners a realistic possibility for NLG applications. To
achieve this quantum leap, all that is needed are a few minor
implementation fixes in FF's preprocessor, and basic reconfiguration
of its search options. While these changes certainly are no
contribution to planning in their own right, we consider it a valuable
-- and slightly unsettling -- lesson learned that such banalities can
make the difference between success and failure. They can hold up
progress in planning applications for years, unless users of a planner
have direct access to its developer. We interpret this as a strong
call for more research on automated configuration techniques,
e.g.\ along the lines of Hutter et al.\ \shortcite{HutHooStu07}. The
detrimental effect of preprocessing details also sheds a light on the
importance of this often neglected part of the planning process.

%illustrative of the
%importance of implementation details such as the preprocessor for the
%overall runtime, and as a strong call for automated configuration
%techniques, e.g.\ along the lines of Hutter et
%al.\ \shortcite{HutHooStu07}.
